Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-29 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

>>>>

% Abschnitt weitere Korrelationen (indirekte)

Beside these more or less \emph{direct} combinations and correlations, which are displaying images 
obtained by SICM and fluorescence microscopy of the same cell/same region, also \emph{indirect} 
correlations exist. They are showing images under comparable conditions and extent the 
investigation to aspects, which could not be obtained by using one technique alone. Such 
\emph{indirect} correlations were used for investigating the uptake of nanotubes \cite{Lee2013}, 
nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
Nichtsdestotrotz (german)
is it important to mention, that they could just giving hints of correlations, it 
is not directly comparable with investigations of both in the same cell.
